Measuring security performance in the Android ecosystem

### 2015-06-08 dastats.tex
./update.sh

\newcommand{\daEndDate}{2015-05-27}

@@

\newcommand{\daMeanOutstandingVulnerabilities}{$0.549 \pm 2.46e$}

@@

\newcommand{\daSecurityScoreNominal}{2.83}
\newcommand{\daSecurityScore}{$2.83 \pm 0.00$}
\newcommand{\daCurrentMeanInsecurityPercNominal}{85.9\%}
\newcommand{\daCurrentMeanInsecurityPerc}{$85.9 \pm 0.1\%$}
\newcommand{\daCurrentMeanInsecurityPercTwosfNominal}{86\%}
\newcommand{\daCurrentMeanInsecurityPercTwosf}{$86 \pm 0\%$}
\newcommand{\daCurrentMeanSecurityPercNominal}{14.1\%}
\newcommand{\daCurrentMeanSecurityPerc}{$14.1 \pm 0.1\%$}
\newcommand{\daCurrentMeanSecurityPercTwosfNominal}{14\%}
\newcommand{\daCurrentMeanSecurityPercTwosf}{$14 \pm 0\%$}
\newcommand{\daCurrentVulnFreeNominal}{0.141}
\newcommand{\daCurrentVulnFree}{$0.141 \pm 0.001$}
\newcommand{\daCurrentMeanOutstandingVulnerabilities}{$0.201 \pm 1.16e$}
\newcommand{\daCurrentUpdatednessNominal}{0.0322}
\newcommand{\daCurrentUpdatedness}{$0.0322 \pm 0.0007$}
\newcommand{\daCurrentUpdatednessPercNominal}{3.22\%}
\newcommand{\daCurrentUpdatednessPerc}{$3.22 \pm 0.07\%$}
\newcommand{\daCurrentUpdatednessPercTwosfNominal}{3.2\%}
\newcommand{\daCurrentUpdatednessPercTwosf}{$3.2 \pm 0.0\%$}
\newcommand{\daCurrentSecurityScoreNominal}{3.36}
\newcommand{\daCurrentSecurityScore}{$3.36 \pm 0.00$}

@@

\newcommand{\daDailyParticipation}{$903 \pm 229$}

@@

\newcommand{\daNumFullVersionUpdates}{4\,530}
\newcommand{\daNumOSVersionUpdates}{3\,840}

@@

\newcommand{\daOSCurveFitParamSecond}{\num{0.0029}}

@@

\newcommand{\daOSCurveFullDeployedYearsNominal}{3.06}
\newcommand{\daOSCurveFullDeployedYears}{$3.06 \pm 70$}

@@

\newcommand{\daAPICurveFitParamSecond}{\num{0.0029}}

@@

\newcommand{\daTabSecScoresmanufacturer}{\begin{table*} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{score} \\ &&&& (out of 10) \\ \hline LG & $0.20 \pm 0.00$ & $0.32 \pm 0.00$ & $0.64 \pm 0.01$ & $3.83 \pm 0.02$ \\  Motorola & $0.17 \pm 0.00$ & $0.12 \pm 0.00$ & $0.73 \pm 0.02$ & $3.03 \pm 0.02$ \\  Samsung & $0.13 \pm 0.00$ & $0.04 \pm 0.00$ & $0.63 \pm 0.00$ & $2.72 \pm 0.00$ \\  Sony & $0.13 \pm 0.00$ & $0.19 \pm 0.00$ & $1.09 \pm 0.02$ & $2.61 \pm 0.02$ \\  HTC & $0.14 \pm 0.00$ & $0.09 \pm 0.00$ & $0.89 \pm 0.01$ & $2.58 \pm 0.02$ \\  asus & $0.19 \pm 0.00$ & $0.52 \pm 0.01$ & $6.01 \pm 0.07$ & $2.31 \pm 0.02$ \\  other & $0.06 \pm 0.00$ & $0.04 \pm 0.00$ & $1.04 \pm 0.01$ & $1.94 \pm 0.02$ \\  Symphony & $0.00 \pm 0.00$ & $0.07 \pm 0.00$ & $5.00 \pm 0.04$ & $0.27 \pm 0.01$ \\  walton & $0.00 \pm 0.00$ & $0.08 \pm 0.00$ & $5.96 \pm 0.08$ & $0.25 \pm 0.01$ \\ \end{tabular} \caption{Security scores for manufacturers} \label{tab:sec_manufacturer} \end{table*}}

@@

\newcommand{\daSecScoreBestmanufacturerScoreNominal}{3.83}
\newcommand{\daSecScoreBestmanufacturerScore}{$3.83 \pm 0.02$}

@@

\newcommand{\daTabSecScoresmodel}{\begin{table*} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{score} \\ &&&& (out of 10) \\ \hline Galaxy Nexus & $0.51 \pm 0.00$ & $0.55 \pm 0.01$ & $1.53 \pm 0.04$ & $4.74 \pm 0.04$ \\  Nexus 4 & $0.28 \pm 0.00$ & $0.82 \pm 0.01$ & $6.06 \pm 0.09$ & $3.59 \pm 0.04$ \\  Nexus 7 & $0.24 \pm 0.00$ & $0.74 \pm 0.01$ & $5.92 \pm 0.09$ & $3.18 \pm 0.04$ \\  other & $0.09 \pm 0.00$ & $0.14 \pm 0.00$ & $0.55 \pm 0.00$ & $2.98 \pm 0.00$ \\  Desire HD & $0.08 \pm 0.00$ & $0.05 \pm 0.00$ & $0.39 \pm 0.02$ & $2.91 \pm 0.04$ \\  HTC Sensation & $0.35 \pm 0.00$ & $0.01 \pm 0.01$ & $1.59 \pm 0.05$ & $2.42 \pm 0.05$ \\  GT-I9100 & $0.22 \pm 0.00$ & $0.02 \pm 0.00$ & $1.23 \pm 0.02$ & $2.28 \pm 0.02$ \\  HTC Desire S & $0.02 \pm 0.00$ & $0.02 \pm 0.00$ & $1.00 \pm 0.06$ & $1.75 \pm 0.07$ \\  GT-N7000 & $0.25 \pm 0.00$ & $0.00 \pm 0.00$ & $2.52 \pm 0.05$ & $1.43 \pm 0.02$ \\  GT-P1000 & $0.01 \pm 0.00$ & $0.00 \pm 0.01$ & $1.79 \pm 0.06$ & $0.90 \pm 0.05$ \\  GT-I9300 & $0.13 \pm 0.00$ & $0.01 \pm 0.00$ & $6.25 \pm 0.04$ & $0.58 \pm 0.01$ \\  GT-I9505 & $0.01 \pm 0.00$ & $0.13 \pm 0.00$ & $6.82 \pm 0.07$ & $0.44 \pm 0.01$ \\  HTC Desire HD & $0.00 \pm 0.00$ & $0.00 \pm 0.01$ & $3.05 \pm 0.05$ & $0.27 \pm 0.03$ \\  GT-N7100 & $0.06 \pm 0.00$ & $0.00 \pm 0.01$ & $6.91 \pm 0.08$ & $0.25 \pm 0.02$ \\  Symphony W68 & $0.00 \pm 0.00$ & $0.00 \pm 0.01$ & $11.00 \pm 0.12$ & $0.00 \pm 0.03$ \\ \end{tabular} \caption{Security scores for models} \label{tab:sec_model} \end{table*}}

@@

\newcommand{\daSecScoreWorstmodelScore}{$0.0001 \pm 0.0276$}

@@

\newcommand{\daTabSecScoressummary}{\begin{table*} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{score} \\ &&&& (out of 10) \\ \hline nexus & $0.37 \pm 0.00$ & $0.47 \pm 0.00$ & $0.59 \pm 0.01$ & $5.06 \pm 0.02$ \\  notnexus & $0.10 \pm 0.00$ & $0.02 \pm 0.00$ & $0.55 \pm 0.00$ & $2.66 \pm 0.00$ \\ \end{tabular} \caption{Security scores for nexus} \label{tab:sec_summary} \end{table*}}
\newcommand{\daTabSecScoresoperator}{\begin{table*} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{score} \\ &&&& (out of 10) \\ \hline O2 uk & $0.26 \pm 0.00$ & $0.12 \pm 0.00$ & $0.37 \pm 0.02$ & $3.84 \pm 0.03$ \\  T-Mobile & $0.21 \pm 0.00$ & $0.18 \pm 0.00$ & $0.42 \pm 0.02$ & $3.73 \pm 0.03$ \\  Orange & $0.21 \pm 0.00$ & $0.09 \pm 0.00$ & $0.39 \pm 0.03$ & $3.52 \pm 0.04$ \\  Sprint & $0.18 \pm 0.00$ & $0.11 \pm 0.00$ & $0.40 \pm 0.02$ & $3.46 \pm 0.03$ \\  3 & $0.18 \pm 0.00$ & $0.09 \pm 0.00$ & $0.52 \pm 0.03$ & $3.23 \pm 0.04$ \\  Vodafone uk & $0.13 \pm 0.00$ & $0.13 \pm 0.00$ & $0.50 \pm 0.03$ & $3.18 \pm 0.04$ \\  AT\&T & $0.13 \pm 0.00$ & $0.08 \pm 0.00$ & $0.43 \pm 0.02$ & $3.09 \pm 0.02$ \\  Verizon & $0.18 \pm 0.00$ & $0.09 \pm 0.00$ & $0.82 \pm 0.02$ & $2.83 \pm 0.02$ \\  unknown & $0.11 \pm 0.00$ & $0.20 \pm 0.00$ & $0.87 \pm 0.02$ & $2.80 \pm 0.02$ \\  n Telenor & $0.03 \pm 0.00$ & $0.12 \pm 0.00$ & $1.25 \pm 0.02$ & $1.81 \pm 0.02$ \\  Airtel & $0.05 \pm 0.00$ & $0.03 \pm 0.00$ & $1.62 \pm 0.03$ & $1.28 \pm 0.03$ \\  Robi & $0.00 \pm 0.00$ & $0.08 \pm 0.00$ & $2.08 \pm 0.04$ & $0.90 \pm 0.03$ \\  Grameenphone & $0.00 \pm 0.00$ & $0.04 \pm 0.00$ & $2.03 \pm 0.02$ & $0.85 \pm 0.01$ \\  banglalink & $0.00 \pm 0.00$ & $0.04 \pm 0.00$ & $2.61 \pm 0.04$ & $0.54 \pm 0.02$ \\ \end{tabular} \caption{Security scores for operators} \label{tab:sec_operator} \end{table*}}

@@

\newcommand{\daSecScoreBestoperatorScoreNominal}{3.84}
\newcommand{\daSecScoreBestoperatorScore}{$3.84 \pm 0.02$}
\newcommand{\daSecScoreBestoperatorNumFullVersions}{97}

@@

\newcommand{\daSecScoreWorstoperatorScoreNominal}{0.535}
\newcommand{\daSecScoreWorstoperatorScore}{$0.535 \pm 0.017$}
\newcommand{\daSecScoreWorstoperatorNumFullVersions}{71}
\newcommand{\daTabDLDistances}{\begin{table} \centering \begin{tabular}{l|c|c|c|c} & manufacturer & model & operator & summary \\ \hline equal & 0.0 & 0.0 & 0.0714 & 0.0 \\weight $m$ & 0.222 & 0.333 & 0.143 & 0.0 \\$f$ & 0.444 & 0.733 & 0.429 & 0.0 \\weight $u$ & 0.444 & 0.133 & 0.214 & 0.0 \\$m$ & 0.667 & 0.733 & 0.357 & 0.5 \\$u$ & 0.778 & 0.733 & 0.714 & 0.0 \\\end{tabular} \caption{Normalised Damerau-Levenshtein distances for different metrics} \label{tab:dl_distances} \end{table}}
\newcommand{\daTabChangeInScores}{\begin{table*} \centering \begin{tabular}{l|c|c|c|c} & manufacturer & model & operator & summary \\ \hline $m$ & $-1.9 \pm 2.2$ & $-0.666 \pm 2.51$ & $-3.27 \pm 1.39$ & $-3.37 \pm 1.83$ \\weight $m$ & $-0.295 \pm 0.274$ & $-0.102 \pm 0.316$ & $-0.458 \pm 0.177$ & $-0.487 \pm 0.209$ \\equal & $-0.116 \pm 0.065$ & $-0.039 \pm 0.113$ & $-0.146 \pm 0.049$ & $-0.166 \pm 0.028$ \\weight $u$ & $-0.0526 \pm 0.127$ & $-0.0152 \pm 0.239$ & $0.02 \pm 0.07$ & $-0.012 \pm 0.125$ \\$u$ & $0.516 \pm 1.61$ & $0.198 \pm 2.14$ & $1.51 \pm 0.96$ & $1.38 \pm 1.5$ \\$f$ & $1.04 \pm 0.58$ & $0.351 \pm 1.02$ & $1.31 \pm 0.44$ & $1.5 \pm 0.2$ \\\end{tabular} \caption{Mean change in scores for different metrics} \label{tab:change_in_scores} \end{table*}}

@@

\newcommand{\daNumUpdatesBigUpgrades}{819}

@@

\newcommand{\daNumDataPoints}{157 Billion}

@@

\newcommand{\daMeanOutstandingVulnerabilitiesNominal}{0.549}
\newcommand{\daCurrentMeanOutstandingVulnerabilitiesNominal}{0.201}

@@

\newcommand{\daMeanOutstandingProbability}{1\%}

>>>>

\newcommand{\daEndDate}{2015-05-31}

@@

\newcommand{\daMeanOutstandingVulnerabilities}{$0.547 \pm 2.45e$}

@@

\newcommand{\daSecurityScoreNominal}{2.84}
\newcommand{\daSecurityScore}{$2.84 \pm 0.00$}
\newcommand{\daCurrentMeanInsecurityPercNominal}{85.4\%}
\newcommand{\daCurrentMeanInsecurityPerc}{$85.4 \pm 0.1\%$}
\newcommand{\daCurrentMeanInsecurityPercTwosfNominal}{85\%}
\newcommand{\daCurrentMeanInsecurityPercTwosf}{$85 \pm 0\%$}
\newcommand{\daCurrentMeanSecurityPercNominal}{14.6\%}
\newcommand{\daCurrentMeanSecurityPerc}{$14.6 \pm 0.1\%$}
\newcommand{\daCurrentMeanSecurityPercTwosfNominal}{15\%}
\newcommand{\daCurrentMeanSecurityPercTwosf}{$15 \pm 0\%$}
\newcommand{\daCurrentVulnFreeNominal}{0.146}
\newcommand{\daCurrentVulnFree}{$0.146 \pm 0.001$}
\newcommand{\daCurrentMeanOutstandingVulnerabilities}{$0.193 \pm 1.11e$}
\newcommand{\daCurrentUpdatednessNominal}{0.0326}
\newcommand{\daCurrentUpdatedness}{$0.0326 \pm 0.0006$}
\newcommand{\daCurrentUpdatednessPercNominal}{3.26\%}
\newcommand{\daCurrentUpdatednessPerc}{$3.26 \pm 0.06\%$}
\newcommand{\daCurrentUpdatednessPercTwosfNominal}{3.3\%}
\newcommand{\daCurrentUpdatednessPercTwosf}{$3.3 \pm 0.0\%$}
\newcommand{\daCurrentSecurityScoreNominal}{3.39}
\newcommand{\daCurrentSecurityScore}{$3.39 \pm 0.00$}

@@

\newcommand{\daDailyParticipation}{$903 \pm 227$}

@@

\newcommand{\daNumFullVersionUpdates}{4\,540}
\newcommand{\daNumOSVersionUpdates}{3\,850}

@@

\newcommand{\daOSCurveFitParamSecond}{\num{0.00289}}

@@

\newcommand{\daOSCurveFullDeployedYearsNominal}{3.07}
\newcommand{\daOSCurveFullDeployedYears}{$3.07 \pm 70$}

@@

\newcommand{\daAPICurveFitParamSecond}{\num{0.00289}}

@@

\newcommand{\daTabSecScoresmanufacturer}{\begin{table*} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{score} \\ &&&& (out of 10) \\ \hline LG & $0.20 \pm 0.00$ & $0.33 \pm 0.00$ & $0.63 \pm 0.01$ & $3.86 \pm 0.02$ \\  Motorola & $0.18 \pm 0.00$ & $0.13 \pm 0.00$ & $0.73 \pm 0.02$ & $3.03 \pm 0.02$ \\  Samsung & $0.13 \pm 0.00$ & $0.04 \pm 0.00$ & $0.63 \pm 0.00$ & $2.72 \pm 0.00$ \\  Sony & $0.13 \pm 0.00$ & $0.19 \pm 0.00$ & $1.09 \pm 0.02$ & $2.61 \pm 0.02$ \\  HTC & $0.14 \pm 0.00$ & $0.09 \pm 0.00$ & $0.89 \pm 0.01$ & $2.58 \pm 0.02$ \\  asus & $0.19 \pm 0.00$ & $0.52 \pm 0.01$ & $6.01 \pm 0.07$ & $2.32 \pm 0.02$ \\  other & $0.06 \pm 0.00$ & $0.04 \pm 0.00$ & $1.03 \pm 0.01$ & $1.95 \pm 0.02$ \\  Symphony & $0.00 \pm 0.00$ & $0.08 \pm 0.00$ & $5.00 \pm 0.05$ & $0.28 \pm 0.01$ \\  walton & $0.00 \pm 0.00$ & $0.08 \pm 0.00$ & $5.96 \pm 0.08$ & $0.25 \pm 0.01$ \\ \end{tabular} \caption{Security scores for manufacturers} \label{tab:sec_manufacturer} \end{table*}}

@@

\newcommand{\daSecScoreBestmanufacturerScoreNominal}{3.86}
\newcommand{\daSecScoreBestmanufacturerScore}{$3.86 \pm 0.02$}

@@

\newcommand{\daTabSecScoresmodel}{\begin{table*} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{score} \\ &&&& (out of 10) \\ \hline Galaxy Nexus & $0.51 \pm 0.00$ & $0.55 \pm 0.01$ & $1.53 \pm 0.04$ & $4.74 \pm 0.04$ \\  Nexus 4 & $0.28 \pm 0.00$ & $0.82 \pm 0.01$ & $6.06 \pm 0.09$ & $3.61 \pm 0.04$ \\  Nexus 7 & $0.24 \pm 0.00$ & $0.74 \pm 0.01$ & $5.92 \pm 0.09$ & $3.19 \pm 0.04$ \\  other & $0.09 \pm 0.00$ & $0.14 \pm 0.00$ & $0.55 \pm 0.00$ & $2.98 \pm 0.00$ \\  Desire HD & $0.08 \pm 0.00$ & $0.05 \pm 0.00$ & $0.39 \pm 0.02$ & $2.91 \pm 0.04$ \\  HTC Sensation & $0.34 \pm 0.00$ & $0.01 \pm 0.01$ & $1.59 \pm 0.05$ & $2.41 \pm 0.05$ \\  GT-I9100 & $0.22 \pm 0.00$ & $0.02 \pm 0.00$ & $1.23 \pm 0.02$ & $2.28 \pm 0.02$ \\  HTC Desire S & $0.02 \pm 0.00$ & $0.02 \pm 0.00$ & $1.00 \pm 0.06$ & $1.75 \pm 0.07$ \\  GT-N7000 & $0.25 \pm 0.00$ & $0.00 \pm 0.00$ & $2.52 \pm 0.05$ & $1.43 \pm 0.02$ \\  GT-P1000 & $0.01 \pm 0.00$ & $0.00 \pm 0.01$ & $1.79 \pm 0.06$ & $0.90 \pm 0.05$ \\  GT-I9300 & $0.13 \pm 0.00$ & $0.01 \pm 0.00$ & $6.25 \pm 0.04$ & $0.58 \pm 0.01$ \\  GT-I9505 & $0.01 \pm 0.00$ & $0.13 \pm 0.00$ & $6.83 \pm 0.07$ & $0.46 \pm 0.01$ \\  HTC Desire HD & $0.00 \pm 0.00$ & $0.00 \pm 0.01$ & $3.05 \pm 0.05$ & $0.27 \pm 0.03$ \\  GT-N7100 & $0.06 \pm 0.00$ & $0.00 \pm 0.01$ & $6.91 \pm 0.08$ & $0.25 \pm 0.02$ \\  Symphony W68 & $0.00 \pm 0.00$ & $0.00 \pm 0.01$ & $11.00 \pm 0.12$ & $0.00 \pm 0.03$ \\ \end{tabular} \caption{Security scores for models} \label{tab:sec_model} \end{table*}}

@@

\newcommand{\daSecScoreWorstmodelScore}{$0.0001 \pm 0.0275$}

@@

\newcommand{\daTabSecScoressummary}{\begin{table*} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{score} \\ &&&& (out of 10) \\ \hline nexus & $0.38 \pm 0.00$ & $0.47 \pm 0.00$ & $0.58 \pm 0.01$ & $5.07 \pm 0.02$ \\  notnexus & $0.10 \pm 0.00$ & $0.02 \pm 0.00$ & $0.55 \pm 0.00$ & $2.67 \pm 0.00$ \\ \end{tabular} \caption{Security scores for nexus} \label{tab:sec_summary} \end{table*}}
\newcommand{\daTabSecScoresoperator}{\begin{table*} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{score} \\ &&&& (out of 10) \\ \hline O2 uk & $0.26 \pm 0.00$ & $0.12 \pm 0.00$ & $0.37 \pm 0.02$ & $3.85 \pm 0.03$ \\  T-Mobile & $0.21 \pm 0.00$ & $0.18 \pm 0.00$ & $0.42 \pm 0.02$ & $3.73 \pm 0.03$ \\  Orange & $0.21 \pm 0.00$ & $0.09 \pm 0.00$ & $0.39 \pm 0.03$ & $3.52 \pm 0.04$ \\  Sprint & $0.18 \pm 0.00$ & $0.11 \pm 0.00$ & $0.40 \pm 0.02$ & $3.46 \pm 0.03$ \\  3 & $0.18 \pm 0.00$ & $0.09 \pm 0.00$ & $0.52 \pm 0.03$ & $3.24 \pm 0.04$ \\  Vodafone uk & $0.13 \pm 0.00$ & $0.13 \pm 0.00$ & $0.50 \pm 0.03$ & $3.18 \pm 0.04$ \\  AT\&T & $0.13 \pm 0.00$ & $0.08 \pm 0.00$ & $0.43 \pm 0.02$ & $3.10 \pm 0.02$ \\  Verizon & $0.18 \pm 0.00$ & $0.09 \pm 0.00$ & $0.82 \pm 0.02$ & $2.83 \pm 0.02$ \\  unknown & $0.11 \pm 0.00$ & $0.20 \pm 0.00$ & $0.86 \pm 0.02$ & $2.81 \pm 0.02$ \\  n Telenor & $0.03 \pm 0.00$ & $0.12 \pm 0.00$ & $1.25 \pm 0.02$ & $1.82 \pm 0.02$ \\  Airtel & $0.05 \pm 0.00$ & $0.03 \pm 0.00$ & $1.62 \pm 0.03$ & $1.28 \pm 0.03$ \\  Robi & $0.00 \pm 0.00$ & $0.08 \pm 0.00$ & $2.08 \pm 0.04$ & $0.90 \pm 0.03$ \\  Grameenphone & $0.00 \pm 0.00$ & $0.04 \pm 0.00$ & $2.02 \pm 0.02$ & $0.85 \pm 0.01$ \\  banglalink & $0.00 \pm 0.00$ & $0.04 \pm 0.00$ & $2.60 \pm 0.04$ & $0.54 \pm 0.02$ \\ \end{tabular} \caption{Security scores for operators} \label{tab:sec_operator} \end{table*}}

@@

\newcommand{\daSecScoreBestoperatorScoreNominal}{3.85}
\newcommand{\daSecScoreBestoperatorScore}{$3.85 \pm 0.02$}
\newcommand{\daSecScoreBestoperatorNumFullVersions}{96}

@@

\newcommand{\daSecScoreWorstoperatorScoreNominal}{0.545}
\newcommand{\daSecScoreWorstoperatorScore}{$0.545 \pm 0.018$}
\newcommand{\daSecScoreWorstoperatorNumFullVersions}{73}
\newcommand{\daTabDLDistances}{\begin{table} \centering \begin{tabular}{l|c|c|c|c} & manufacturer & model & operator & summary \\ \hline equal & 0.0 & 0.0 & 0.0714 & 0.0 \\weight $m$ & 0.222 & 0.333 & 0.143 & 0.0 \\weight $u$ & 0.444 & 0.133 & 0.214 & 0.0 \\$f$ & 0.444 & 0.733 & 0.5 & 0.0 \\$m$ & 0.667 & 0.733 & 0.357 & 0.5 \\$u$ & 0.778 & 0.733 & 0.714 & 0.0 \\\end{tabular} \caption{Normalised Damerau-Levenshtein distances for different metrics} \label{tab:dl_distances} \end{table}}
\newcommand{\daTabChangeInScores}{\begin{table*} \centering \begin{tabular}{l|c|c|c|c} & manufacturer & model & operator & summary \\ \hline $m$ & $-1.9 \pm 2.2$ & $-0.664 \pm 2.51$ & $-3.27 \pm 1.39$ & $-3.38 \pm 1.83$ \\weight $m$ & $-0.294 \pm 0.275$ & $-0.101 \pm 0.316$ & $-0.458 \pm 0.177$ & $-0.487 \pm 0.209$ \\equal & $-0.116 \pm 0.064$ & $-0.0386 \pm 0.113$ & $-0.146 \pm 0.048$ & $-0.166 \pm 0.029$ \\weight $u$ & $-0.0522 \pm 0.126$ & $-0.0148 \pm 0.238$ & $0.0206 \pm 0.0797$ & $-0.00995 \pm 0.123$ \\$u$ & $0.517 \pm 1.61$ & $0.2 \pm 2.1$ & $1.52 \pm 0.96$ & $1.39 \pm 1.48$ \\$f$ & $1.04 \pm 0.58$ & $0.348 \pm 1.01$ & $1.31 \pm 0.43$ & $1.49 \pm 0.26$ \\\end{tabular} \caption{Mean change in scores for different metrics} \label{tab:change_in_scores} \end{table*}}

@@

\newcommand{\daNumUpdatesBigUpgrades}{820}

@@

\newcommand{\daNumDataPoints}{158 Billion}

@@

\newcommand{\daMeanOutstandingVulnerabilitiesNominal}{0.547}
\newcommand{\daCurrentMeanOutstandingVulnerabilitiesNominal}{0.193}

@@

\newcommand{\daMeanOutstandingProbability}{1.0\%}
